### 2018-10-11 papers/journal/experiments.tex
Added all three result tables and rewritten CBMC first paragraph

We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings. All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
\subsection{SATVTS (Bounded model checker based tool)} 
The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
%
Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
CBMC allows the depth of model to be incrementally increased to any desired value.

CBMC consists of a C-language front-end (CFE) and SAT Solver back-end (SAT).
%
CBMC accepts ANSI-C programs interspersed with special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%		
In our experiments, the vesicle transport network was modeled as a non-deterministic C-program manipulating a graph with labeled edges with the fusion rules and steady state properties expressed as constraints
using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, CBMC verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. CBMC reports successful verification if the formula is found to be valid. If not, then CBMC produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}

>>>>

We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings. All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.

\input{result-table}

\subsection{SATVTS (Bounded model checker based tool)} 
The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
%
CBMC is a Bounded Model Checker for C and C++ programs. 
%
Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.

The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%		
In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, CBMC verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. CBMC reports successful verification if the formula is found to be valid. If not, then CBMC produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}

### 2018-10-11 papers/journal/result-table.tex
Added all three result tables and rewritten CBMC first paragraph

@@

    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
    plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
    sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
    node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
    yeast-graph & 40.225  & 1 E  &   timeout  & N/A   & 1393.84  & 1 E  & 468.161   & 1 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
    mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
  \end{tabular}
    \caption{Run-times for synthesis queries. \#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS. Time is reported in seconds. (a) The solver used is DepQBF (b) The solver used is Z3. The sub-mammal is a subgraph of the complete mammal-graph. In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules. In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}

  % \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
  % Time is reported in seconds.}
  \label{tab:qf-graph}
\end{sidewaysfigure}

%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT

We have implemented the encodings in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS. 
%
The tool can not only synthesize the above-discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
processing formulas. 
%
Since some of the formulas involve alternation of quantifiers over
Boolean variables Z3 is not a suitable choice for those examples.
%
We translate the formulas created by Z3 tool into a standard
QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
%
We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
%
Our tool includes about 7000 lines of code.

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in table~\ref{tab:qf-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
%The experiments were conducted with a 900s timeout.
%
The first four VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}
In the table, we are reporting five synthesis queries
%
The first one only adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
% %
% Our tools were able to complete the graphs by adding five new edges
% and nine new molecules in 210s.
%
The second query adds new labels to the edge.
%  and was able to
% fix the graphs with eleven new molecule labels in 180s.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates for activity functions, while allowing
more edges to be added.
%
The result shows the basic template of 4 leaves and 3 gates.
%
% The tool was able to synthesize the Boolean functions in 470s.
%
To illustrate the versatility of our tool, the fourth query
synthesizes $3$-CNF functions (encoding not presented).
%  and was able to
% synthesis the results for all graphs in 500s.
%
Finally, we report queries that allows both addition and deletion of edges, and labels
of node and labels.

%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\def\arraystretch{1.6}
\caption{
{\bf SNARE regulation and graph connectedness.}}
\begin{tabular}{|c|l|l|c|}
\hline
\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
2. & None & Boolean function & N \& S = 3C\\ \hline
3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
5. & Boolean function & None & No graphs found\\ \hline
6. &  None & None & No graphs found\\ \hline

%6. & Arbitrary Boolean & Specificity matrix and every edge is distinct & N \& S = 3C\\ \hline

\end{tabular}
\label{tab:smt-grph}
%\end{adjustwidth}
\end{table}

\begin{table}[t]
	\centering
	% \def\arraystretch{1.6}
	\begin{tabular}{|c|c|c|c|}
		\hline
		{\multirow{2}{*}{\textbf{Variant}}}  &
		\multicolumn{2}{c|}{\textbf{Constraints}} &
		{\multirow{2}{*}{\textbf{Graph connectivity}}}
		% \multicolumn{2}{c|}{\textbf{Graph connectivity}}
		\\
		\cline{2-3}
		&  \textbf{Rest} & \textbf{Activity} &  % & \textbf{Sampling: Guarantee}
	\\ \hline

	A. & \multirow{5}{*}{
		\makecell{ \ref{eq:f0}--\ref{eq:fuse2},\\
			\ref{eq:reach1},\ref{eq:reach2},\\
			\ref{eq:drop1}--\ref{eq:drop4}}
	}
	& \ref{eq:ann},\ref{eq:aen} & No graph     \\\cline{3-4}
	B. & & \ref{eq:anb},\ref{eq:aen} & No graph     \\\cline{3-4}
	C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected  \\\cline{3-4}
	D. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected  \\\cline{3-4}
	E. & & \ref{eq:ann},\ref{eq:aep} & No graph     \\\cline{3-4}
	F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected  \\\hline

	% C_es :Self edges are allowed
	% C_ed : Every edge is distinct 
\end{tabular}
\caption{{\bf Activity regulation of molecules vs. graph connectivity.
}}
\label{tab:smt-grph}
\end{table}

@@

		plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
		plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
		sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
		node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
		yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
		mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
	\end{tabular}
	\caption{Run-times for synthesis queries. \#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS. Time is reported in seconds. (a) The solver used is DepQBF (b) The solver used is Z3. The sub-mammal is a subgraph of the complete mammal-graph. In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules. In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}

	% \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
	% Time is reported in seconds.}
	\label{tab:qbf-graph}
\end{sidewaysfigure}
